Dataset of operator-client dialogues aligned with knowledge-base queries

### 2016-06-24 paper.tex
latest comments

\begin{abstract}
    This paper presents a novel datasets for training end-to-end task oriented conversational agents.
    The dataset contains task oriented conversation between an operator, a task expert, and a client who is seeking information about the task along with records of data base API calls of the operator, which capture the distilled meaning of the user query.
    The data base calls represent not only instantiation of user wishes but also, when evaluated against the database determine the answer from the database, which were used by the operator to provide requested information to the client. 
    We expect that this additional supervision of recording database interaction will provide enough information so the task of the conversation can be understood and behaviour of the interlocutors reconstructed by software agents.
    The dataset was collected using crowdsourcing in offline setting, where each contributor played role either of an operator or a client and contributed single utterance.
    The quality of the data were enforced by mutual control among contributors and manually verified on random sub-sample.
    The dataset is available for download under the Creative Commons 4.0 BY-SA license.
\end{abstract}

@@

Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data\cite{duvsek2014alex},\cite{raux2005let}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction\cite{young2010hidden,gasic2011line}, and lately are trained using supervised learning typically in end-to-end manner\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
The reinforce learning on one hand need just collect enough live user conversation without any transcription with the exception of explicit feedback at the end of each dialogue, but because the feedback signal is typically rather noise and delayed one require thousands of live conversations to improve rather simple policy.\cite{gasic2011line}
The supervised-learning methods greatly reduced the number of conversation needed for training reasonable policy to few hundreds\cite{wen2016network}, but require annotation for all components used the dialogue which so far included at least a dialogue state\cite{wen2016network, young2010hidden}.
Since the dialogue state is simplification of dialogue history and has no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
In this paper, we focus on collecting supervised training set with rich enough annotation so the supervised models similar to~\cite{wen2016network} can be trained with few hundreds of dialogues, but the annotation of dialogues are much easier to collect.

We believe that the present dataset can be used for first experiments for end-to-end systems using supervised learning without annotated dialogue state.
The resulting systems should be able to roughly compare to systems trained on datasets with \cite{williams2013dstc1, henderson2014dstc2, henderson2014dstc3} dialogue state annotation because the same settings, i.e.\ database and task, for data collection.
Despite the fact, we collected human-to-human dialogues on known task of Cambridge restaurant domains the data-collecting method is completely domain and language independent.

@@

We note that on one hand further annotation of dialogue conversation may help to train the models faster, but simply collecting more data is typically more beneficial even with less annotation for models which does not require such annotation.
As a consequence, we see work of~\cite{wen2016network},~\cite{bordes2016learning} and~\cite{williams2016end} as great step forward since there work use annotation on dialogue state level or even no annotation for training dialogue agents.

On the other hand, we believe that annotating a dialogue state according to expert-handcrafted ontology is both artificial and still very labour intensive data collection task, so our work aim at collecting conversation with lighter but more easier to get annotations.
We suppose that a task-oriented  domain is defined by a task database e.g. in the Cambridge restaurant domain by database containing information about restaurants
We further suppose that there two roles in the conversation a {\it client} and a {\it operator}.
Typically, one wants to train a system which replaces the {\it operator} who is the domain expert.
{\it Clients} seek information stored in the database and use the system instead of human operator to obtain desired information.
In order to collect cheap high quality training data conversation one can record conversation between human operator and human clients.
Typically, the operator is provided with interface to the database so it can quickly find relevant information and play the role of domain expert.
We suggest to collect the operator's database calls with its arguments instead of dialogue state annotation after each turn.

@@

Our data collection processed aimed at collecting natural conversation in the well defined domain.
We selected well studied Cambridge restaurant domain since the previous dataset~\cite{williams2013dstc1, henderson2014dstc2, henderson2014dstc3} in that domain demonstrated that a meaningful and not too long conversation can be held in the domain.
Also it was proven that the domain is on one hand difficult enough that even the state-of-the art systems does not reach human-level performance in the role of the operator and on the other hand numerous systems~\cite{young2010hidden, gasic2011line, wen2016network} demonstrated that are able to provide information to the clients reasonable well.

@@

We used exactly the same database as provided for the DSTC2 challenge.
The database contains information about 107 restaurants and their properties stored in the columns:

% \begin{itemize}
\begin{inparaenum}
    \item name (107),
    \item price range (3?),
    \item area (4),
    \item food (20?),
    \item address (90?),
    \item phone (90?),
    \item postcode (90?).
\end{inparaenum}
% \end{itemize}

We include the size of the vocabulary in brackets for each column.
The address or the postcode are unique for each restaurant but are sometimes missing, but the name of the restaurant is always known. 
There typically multiple restaurant with the same price range, area, or food type property.
These properties are sometimes unknown as well.

We use the database to generate the clients goals as demonstrated in~Figure~\ref{fig:client}, but only the operator is able to search the database (see~Figure~\ref{fig:operator}).

@@

Before submitting a reply the client is instructed to read the dialogue history and marked the goals which were presented to the operator.
The worker in the role of client is paid for each submitted response.

@@

\subsubsection{Operator database}
\label{sec:operator}
The operator is asked to politely reply the clients needs according the information stored in the database.
In order to provide the informations to clients the operator uses the DB interface depicted in~Figure~\ref{fig:operator}.
Her or she filters the restaurants using a full text search on the database.
The content of the database is intentional hidden if no filter is specified so the filter has to be used.
The CF workers are also instructed also explicitly mark the rows of the restaurants about which provide the information in their answer.

@@

@@

Our work is closely related  to work of~\cite{williams2013dstc1, henderson2014dstc2, henderson2014dstc3} in the sense that the conversation are held in the same domain.
On the other hand, the collection process differs substantially because we do not use any artificial system and rather we focus on collecting high quality human conversations. In addition, in our work we do not collect complicated annotation on LU and DST level as it was previously done on DST challenges.

A very relevant work of~\cite{wen2016network} collected human-human dialogues in similar domain to the Cambridge domain according their description.
Their dataset is not yet published so we compare only with their statistics.
The dataset is of similar size and used very similar collection scheme where the Amazon Mechanical Turk workers submitted one reply at a time without being connected to each other in real-time.

@@

\section{Conclusion and Future work}
\label{sec:conc}
We present a new human-human dialogue dataset with annotation of user intension in form of their database calls.
We also introduced a novel data collection setting which resembles work of operators in call centers and introduce minimum overhead to crowdsourcing workers.
The collected dialogues are published under Creative Commons 4.0 BY-SA license on available to download at {\it anonymised}.  % lindat\footnote{todo where}.

@@

\subsubsection*{Acknowledgments}
We would like to thank Ond\v{r}ej Du\v{s}ek for useful comments.
This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333. 
We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Centre CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no. CZ.1.05/3.2.00/08.0144.

>>>>

\begin{abstract}
    This paper presents a novel dataset for training end-to-end task oriented conversational agents.
    The dataset contains task oriented conversations between an operator, a task expert, and a client who is seeking information about the task along with records of data base API calls of the operator, which capture the distilled meaning of the user query.
    The data base calls represent not only instantiation of user wishes but also, when evaluated against the database determine the answer from the database, which were used by the operator to provide requested information to the client. 
    We expect that this additional supervision of recording database interaction will provide enough information so the task of the conversation can be understood and behaviour of the interlocutors reconstructed by software agents.
    The dataset was collected using crowdsourcing in offline setting, where each contributor played role either of an operator or a client and contributed single utterance.
    The quality of the data were enforced by mutual control among contributors and manually verified on random sub-sample.
    The dataset is available for download under the Creative Commons 4.0 BY-SA license.
\end{abstract}

@@

Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data\cite{duvsek2014alex,raux2005let}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction\cite{young2010hidden,gasic2011line}, and lately are trained using supervised learning typically in end-to-end manner\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
The reinforce learning on one hand need just collect enough live user conversation without any transcription with the exception of explicit feedback at the end of each dialogue, but because the feedback signal is typically rather noise and delayed one require thousands of live conversations to improve rather simple policy.\cite{gasic2011line}
The supervised-learning methods greatly reduced the number of conversation needed for training reasonable policy to few hundreds\cite{wen2016network}, but require annotation for all components used the dialogue which so far included at least a dialogue state\cite{wen2016network,young2010hidden}.
Since the dialogue state is simplification of dialogue history and has no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
In this paper, we focus on collecting supervised training set with rich enough annotation so the supervised models similar to~\cite{wen2016network} can be trained with few hundreds of dialogues, but the annotation of dialogues are much easier to collect.

We believe that the present dataset can be used for first experiments for end-to-end systems using supervised learning without annotated dialogue state.
The resulting systems should be able to roughly compare to systems trained on datasets with~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} dialogue state annotation because the same settings, i.e.\ database and task, for data collection.
Despite the fact, we collected human-to-human dialogues on known task of Cambridge restaurant domains the data-collecting method is completely domain and language independent.

@@

We note that further annotation of dialogue conversation may help to train the models faster, but simply collecting more data is typically more beneficial.
As a consequence, we see works~\cite{wen2016network,bordes2016learning,williams2016end} as important step forward since there work use annotation only on dialogue state level or even no annotation at all for training dialogue agents.

On the other hand, we believe that annotating a dialogue state according to expert-handcrafted ontology is both artificial and still very labor-intensive data collection task, so our work aim at collecting conversation with lighter but more easier to get annotations.
We suppose that a task-oriented  domain is defined by a task database e.g. in the Cambridge restaurant domain by database containing information about restaurants. 
We further suppose that there two roles in the conversation a {\it client} and a {\it operator}.
Typically, one wants to train a system which replaces the {\it operator} who is the domain expert.
{\it Clients} seek information stored in the database and use the system instead of human operator to obtain desired information.
In order to collect cheap high quality training data conversation one can record conversation between human operator and human clients.
Typically, the operator is provided with interface to the database so it can quickly find relevant information and play the role of domain expert.
We suggest to collect the operator's database calls with its arguments instead of dialogue state annotation after each turn.

@@

Our data collection processed aimed at collecting natural conversation in the well defined domain.
We selected well studied Cambridge restaurant domain since the previous dataset~\cite{williams2013dstc1,henderson2014dstc2,henderson2014dstc3} in that domain demonstrated that a meaningful and not too long conversation can be held in the domain.
Also it was proven that the domain is on one hand difficult enough that even the state-of-the art systems does not reach human-level performance in the role of the operator and on the other hand numerous systems~\cite{young2010hidden,gasic2011line,wen2016network} demonstrated that are able to provide information to the clients reasonable well.

@@

We used exactly the same database as provided for the DSTC2 challenge.
The database contains information about 107 restaurants and their properties stored in the columns.
We include the size of the vocabulary in brackets for each column:
% \begin{itemize}
\begin{inparaenum}
    \item name (107),
    \item price range (3?),
    \item area (4),
    \item food (20?),
    \item address (90?),
    \item phone (90?),
    \item postcode (90?).
\end{inparaenum}
% \end{itemize}

The address or the postcode are unique for each restaurant but are sometimes missing, but the name of the restaurant is always known. 
There are typically multiple restaurant with the same price range, area, or food type property and these properties might be unknown for a restaurant.

Note that we use the database to generate the clients goals as demonstrated in~Figure~\ref{fig:client} and only the operator is able to search the database add demonstrated in~Figure~\ref{fig:operator}.

@@

Before submitting a reply the client is instructed to read the dialogue history and marked the goals which were presented to the operator.

@@

\subsubsection{Operator database}
\label{sec:operator}
The operator is asked to politely reply the clients needs according the information stored in the database.
In order to provide the information to clients the operator uses the DB interface depicted in~Figure~\ref{fig:operator}.
Her or she filters the restaurants using a full text search on the database.
The content of the database is intentional hidden if no filter is specified so the filter has to be used.
The CF workers are also instructed also explicitly mark the rows of the restaurants about which provide the information in their answer.

@@

The workers are paid for every submitted response the same amount independently if they play client or operator role.
The roles are assigned independently.

@@

Our work is closely related  to work of~\cite{williams2013dstc1, henderson2014dstc2, henderson2014dstc3} in the sense that the conversation are held in the same domain.
On the other hand, the collection process differs substantially because we do not use any artificial system and rather we focus on collecting high quality human conversations. In addition, in our work we do not collect complicated annotations on LU and DST level.

A~relevant work of~\cite{wen2016network} collected human-human dialogues in similar domain to the Cambridge domain according their description.
Their dataset is not yet published so we compare only with their statistics.
The dataset is of similar size and used very similar collection scheme where the Amazon Mechanical Turk workers submitted one reply at a time without being connected to each other in real-time.

@@

\section{Conclusion and Future work}
\label{sec:conc}
We present a new human-human dialogue dataset with annotation of user intention in form of their database calls.
We also introduced a novel data collection setting which resembles work of operators in call centers and introduce minimum overhead to crowdsourcing workers.
The collected dialogues are published under Creative Commons 4.0 BY-SA license on available to download at {\it anonymized}.  % lindat\footnote{todo where}.

@@

\subsubsection*{Acknowledgments}
We would like to thank Ond\v{r}ej Du\v{s}ek for useful comments.
This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333. 
We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no. CZ.1.05/3.2.00/08.0144.
